---
title: "Coursera Project FARS Vignette"
author: "Milan de Vries"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Coursera Project FARS Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo=FALSE, message=FALSE, include=FALSE}
library(courserafars)
library(dplyr)
library(maps)
```

## Intro

This document introduces you to the basics of this package. This packages provides a set of functions to analyze accident data files created by the National Highway Traffic Safety Administration [NHTSA](https://nhtsa.gov/). The files record fatal motor vehicle accidents in the United States. 

## Summarizing Accidents

One main function of this package is to summarize accident data by month, across years. This is done with the `fars_summarize_years()` function, which takes a vector or list of years and outputs a comparison table. Note that the accident data files must be in the working director of the session.

```{r}
setwd(system.file("extdata", package = "courserafars"))
fars_summarize_years(c(2013,2014))
```

## Plotting Accidents

This package also allows you to visualize accidents in a given year in a given state. This is done through the `fars_map_state()` function. For instance, in the following example, we plot all of the accidents in Florida for the year 2014.

```{r, warning = FALSE, message = FALSE, fig.width = 8}
setwd(system.file("extdata", package = "courserafars"))
fars_map_state(12,2014)
```
